The "Back Burner Brew" is built with the sole purpose of brewing large batch of beer in the home environment. This product provides home brewers with a low-cost electric home brewing system that allow them to have precise control over the brewing process. The brewing process can be automated with the help of micro-controllers like the ESP32 which is then hosted to a local website or an app interface.

ESP32 is a micro-controller that can receive data such as current temperature of the water or mash from the heat sensors located inside the kettles which can be converted to either analog or digital input. The heating coil can be controled using the input from the user as per their desired either to increase or to decrease the temperature. The electric pump can also be controlled by the user through micro-controllers to regulate the flow of the water in the kettles. The user will be able to communicate with the brewing system through a web interface or app interface.

The user should expect to input desired commands, controls, and specific
settings such as temperature and length of time by a easily accessible
touchscreen. The touchscreen will be attached to a Raspberry Pi that will handle
communications between the user and the various sensors and heating elements.
The user can expect that whichever temperature they set for their desired
application, that the temperature will remain constant.

The intended audiences for this product would be home brewers or person interested in brewing beer only. Provided that the user manual would be present in the product, any person who wants to brew beer in his local environment can easily use this product. This product is made focusing on how effortless can the brewing process gets simply with the use of micro-controller.